Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.tex
revised experiment section

Experiment I is designed to study the ability of human subjects to
detect the effect of a non-linear term \(\boldsymbol{z}\) constructed
using Hermite polynomials {[}Hermite ref here{]} on random vector
\(\boldsymbol{x}\) formulated as

@@

\caption{\label{tab:model-factor-table}Description of all factors involved in the nonlinear and heteroskedasticity studies.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rcrrrr}
\toprule
\multicolumn{1}{c}{Poly Order ($j$)} & \multicolumn{1}{c}{\makecell[c]{Distribution of $X_{raw}$\\}} & \multicolumn{1}{c}{SD ($\sigma$)} & \multicolumn{1}{c}{Poly Shape ($a$)} & \multicolumn{1}{c}{Heteroskedasticity ($b$)} & \multicolumn{1}{c}{Size ($n$)} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
2 & $U(-1, 1)$ & 0.25 & -1 & 0.25 & 50\\
3 & $N(0, 0.3^2)$ & 1.00 & 0 & 1.00 & 100\\
6 & $lognormal(0, 0.6^2)/3$ & 2.00 & 1 & 4.00 & 300\\
18 & $U\{1, 5\}$ & 4.00 &  & 16.00 & \\
 & NA &  &  & 64.00 & \\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{Variations in fitted values, that might affect perception of residual plots. Four different distribution of $x_{raw}$ are used in the experiment to provide various visual patterns.}\label{fig:different-dist}
\end{figure}

Figure \ref{fig:example-poly-lineup} shows one of the lineups used in
experiment I. This lineup was produced under \(j = 6\) and
\(X_{raw} \sim N(0.0.3^2)\). The actual data plot location was four. All
five subjects correctly identified the actual data plot for this lineup.

@@

For \(b \neq 0\), the variance-covariance matrix of the error term
\(\boldsymbol{\varepsilon}\) is correlated with the regressor \(x\),
which will lead to the presence of heteroskedasticity. Visual patterns
were simulated using three different shapes (\(a\) = -1, 0, 1) and the
same four different distribution of \(X_{raw}\) used in experiment I. A
summary of the factors is given in Table \ref{tab:model-factor-table}.

@@

An example lineup of this model is shown in Figure
\ref{fig:example-heter-lineup} with \(a = -1\) and
\(X_{raw} \sim U(-1, 1)\). The actual data plot location was 15. 8 out
of 11 subjects correctly identified the actual data plot for this
lineup.

\hypertarget{experimental-setup}{%
\subsection{Experimental setup}\label{experimental-setup}}

@@

As summarised in Table \ref{tab:model-factor-table}, three additional
parameters \(n\), \(\sigma\) and \(b\) were used to control the strength
of the signal so that different difficulty levels of lineups were
generated, and therefore, the estimated power curve would be smooth and
continuous. Parameter \(\sigma \in \{0.5, 1, 2, 4\}\) and
\(b \in \{0.25, 1, 4, 16, 64\}\) were used in experiment I and II
respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b}
demonstrate the impact of these two parameters. A large value of
\(\sigma\) will increase the variation of the error of the non-linear
model and decrease the visibility of the visual pattern. The parameter
\(b\) controls the ratio of the standard deviation of the
heteroskedasticity across the domain of the regressor. Given
\(x \neq a\), a larger value of \(b\) will lead to a larger ratio of the
variance at \(x\) to the variance at \(x - a = 0\), making the visual
pattern more obvious.

@@

Three replications are made for each of the parameter values shown in
Table \ref{tab:parameter-table} resulting in
\((4 \times 4 \times 4 \times 3 + 4 \times 3 \times 5 \times 3) \times 3 = 1116\)
different lineups. In addition, each lineup is designed to be evaluated
by five different subjects. After attempting some pilot studies
internally in our research group, we decide to present a block of 20
lineups to every subject. And to ensure the quality of the survey data,
two lineups with obvious visual patterns are included as attention
checks. Thus, \(576 \times 5/(20-2) = 160\) and
\(540 \times 5 /(20-2) = 150\) subjects were recruited to satisfy the
design of the experiment I and experiment II respectively.

As mentioned in Section {[}the alpha section{]}, \(\alpha\) used in
Equation \ref{eq:eq:pvalue-beta-binomial} needs to be estimated using
Rorschach lineups. Hence, 36 Rorschach lineups with all combinations of
\(n\) and \(X_{raw}\) and three replications are designed to be included
in experiment III. All Rorschach lineups are planned to be evaluated by
20 subjects. However, presenting only Rorschach lineups to subjects are
considered to be bad practices as subjects will lose interest quickly.
We planned to also collect 6 more evaluations on the 279 lineups with
uniform distribution, resulted in
\((36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3)/(20-2) = 133\)
subjects recruited for experiment III.

@@

Subjects for all three experiments were recruited from an crowdsourcing
platform called Prolific {[}ref here{]}. Prescreening procedure was
applied during the recruitment, subjects were required to be fluent in
English, with \(98\%\) minimum approval rate in other studies and 10
minimum submissions. During the experiment, every subject was presented
with a block of 20 lineups. For each lineup, the actual data plot was
drawn as a standard residual plot of the null model with raw residuals
on the y-axis and fitted values on the x-axis. An additional horizontal
red line was added at \(y = 0\) as a helping line. The 19 null datasets
were generated by the residual rotation technique, and plotted in the
same way. The lineup consisted of 20 residual plots with one randomly
placed actual data plot. And for every lineup, the subject was asked to
select one or more plots that are most different from others, provide a
reason for their selections, and evaluate how different they think the
selected plots were from others. If there was no noticeable difference
between plots in a lineup, subjects were permitted to select zero plots
without providing the reason. No subject was shown the same lineup
twice. Information about preferred pronoun, age group, education, and
previous experience in visual experiment were also collected. A
subject's submission was only accepted if the actual data plot was
identified for at least one attention check. Data of rejected
submissions were discarded automatically to maintain the overall data
quality.

>>>>

Experiment I is designed to study the ability of human subjects to
detect the effect of a non-linear term \(\boldsymbol{z}\) constructed
using Hermite polynomials {[}unsure how to cite 1810 work{]} on random
vector \(\boldsymbol{x}\) formulated as

@@

\caption{\label{tab:model-factor-table}Description of all factors involved in the non-linear and heteroskedasticity studies.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rcrrrr}
\toprule
\multicolumn{1}{c}{Poly Order ($j$)} & \multicolumn{1}{c}{\makecell[c]{Distribution of $X_{raw}$\\}} & \multicolumn{1}{c}{SD ($\sigma$)} & \multicolumn{1}{c}{Heteroskedasticity Shape ($a$)} & \multicolumn{1}{c}{Heteroskedasticity ($b$)} & \multicolumn{1}{c}{Size ($n$)} \\
\cmidrule(l{3pt}r{3pt}){1-1} \cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6}
2 & $U(-1, 1)$ & 0.25 & -1 & 0.25 & 50\\
3 & $N(0, 0.3^2)$ & 1.00 & 0 & 1.00 & 100\\
6 & $lognormal(0, 0.6^2)/3$ & 2.00 & 1 & 4.00 & 300\\
18 & $U\{1, 5\}$ & 4.00 &  & 16.00 & \\
 &  &  &  & 64.00 & \\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{Variations in fitted values, that might affect perception of residual plots. Four different distribution of $X_{raw}$ are used in the experiment to provide various visual patterns.}\label{fig:different-dist}
\end{figure}

Figure \ref{fig:example-poly-lineup} shows one of the lineups used in
experiment I. This lineup is produced under \(j = 6\) and
\(X_{raw} \sim N(0.0.3^2)\). The actual data plot location is
\(2^3 - 4\). All five subjects correctly identified the actual data plot
for this lineup.

@@

For \(b \neq 0\), the variance-covariance matrix of the error term
\(\boldsymbol{\varepsilon}\) is correlated with the regressor
\(\boldsymbol{x}\), which will lead to the presence of
heteroskedasticity. Visual patterns were simulated using three different
shapes (\(a\) = -1, 0, 1) and the same four different distribution of
\(X_{raw}\) used in experiment I. A summary of the factors is given in
Table \ref{tab:model-factor-table}.

@@

An example lineup of this model is shown in Figure
\ref{fig:example-heter-lineup} with \(a = -1\) and
\(X_{raw} \sim U(-1, 1)\). The actual data plot location is \(2^4 + 2\).
Nine out of 11 subjects correctly identified the actual data plot for
this lineup.

\hypertarget{experiment-setup}{%
\subsection{Experiment setup}\label{experiment-setup}}

@@

As summarised in Table \ref{tab:model-factor-table}, three additional
parameters \(n\), \(\sigma\) and \(b\) were used to control the strength
of the signal so that different difficulty levels of lineups were
generated, and therefore, the estimated power curve would be smooth and
continuous. Parameter \(\sigma \in \{0.5, 1, 2, 4\}\) and
\(b \in \{0.25, 1, 4, 16, 64\}\) were used in experiment I and II
respectively. Figure \ref{fig:different-sigma} and \ref{fig:different-b}
demonstrate the impact of these two parameters. A large value of
\(\sigma\) will increase the variation of the error of the non-linearity
model and decrease the visibility of the visual pattern. The parameter
\(b\) controls the ratio of the standard deviation of the
heteroskedasticity across the domain of the regressor. Given
\(x \neq a\), a larger value of \(b\) will lead to a larger ratio of the
variance at \(x\) to the variance at \(x - a = 0\), making the visual
pattern more obvious.

@@

Three replications were made for each of the parameter values shown in
Table \ref{tab:model-factor-table} resulting in
\((4 \times 4 \times 4 \times 3 + 4 \times 3 \times 5 \times 3) \times 3 = 1116\)
different lineups. In addition, each lineup was designed to be evaluated
by five different subjects. After attempting some pilot studies
internally in our research group, we decided to present a block of 20
lineups to every subject. And to ensure the quality of the survey data,
two lineups with obvious visual patterns were included as attention
checks. Thus, \(576 \times 5 \div (20-2) = 160\) and
\(540 \times 5 \div (20-2) = 150\) subjects were recruited to satisfy
the design of the experiment I and experiment II respectively.

As mentioned in Section \ref{calculating-p-values}, \(\alpha\) used in
Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using
Rorschach lineups. Hence, 36 lineups consist of only null plots with all
combinations of \(n\) and \(X_{raw}\) and three replications are
designed to be included in experiment III. Note that we generated the
lineups using the same simulation mechanism discussed in Section
\ref{sampling-from-the-null-distribution} rather than from a null model.
We overlooked this detail until the data had been collected. Thus, we
used another valid method suggested in vanderplas2021statistical which
was designed for typical lineups to estimate \(\alpha\) correctly.
However, by not using Rorschach lineups, we did lose some accuracy in
the estimation. We recommend future studies to generate Rorschach
lineups strictly following the definition given by
buja\_statistical\_2009.

All lineups consist of only null plots are planned to be evaluated by 20
subjects. However, presenting only these lineups to subjects are
considered to be bad practices as subjects will lose interest quickly.
We planned to also collect 6 more evaluations on the 279 lineups with
\(X_{raw} \sim U(-1,1)\), resulted in
\((36 \times 20 + (4 \times 4 \times 3 + 3 \times 5 \times 3) \times 3) \div (20-2) = 133\)
subjects recruited for experiment III.

@@

Subjects for all three experiments were recruited from an crowdsourcing
platform called Prolific {[}palan2018prolific{]}. Prescreening procedure
was applied during the recruitment, subjects were required to be fluent
in English, with \(98\%\) minimum approval rate in other studies and 10
minimum submissions. During the experiment, every subject was presented
with a block of 20 lineups. For each lineup, the actual data plot was
drawn as a standard residual plot of the null model with raw residuals
on the y-axis and fitted values on the x-axis. An additional horizontal
red line was added at \(y = 0\) as a helping line. The 19 null datasets
were generated by the residual rotation technique, and plotted in the
same way. The lineup consisted of 20 residual plots with one randomly
placed actual data plot. And for every lineup, the subject was asked to
select one or more plots that are most different from others, provide a
reason for their selections, and evaluate how different they think the
selected plots were from others. If there was no noticeable difference
between plots in a lineup, subjects were permitted to select zero plots
without providing the reason. No subject was shown the same lineup
twice. Information about preferred pronoun, age group, education, and
previous experience in visual experiment were also collected. A
subject's submission was only accepted if the actual data plot was
identified for at least one attention check. Data of rejected
submissions were discarded automatically to maintain the overall data
quality.
